---
title: "Cabbages"
author: "Karla Cota Lopez"
date: "October 1, 2024"
output:
  html_document:
    df_print: paged
---

```{r include=FALSE,echo=FALSE}
require(tidyverse)
require(tigerstats)
require(MASS)
veggy <- cabbages
```

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?!-->
 The cabbages data from the MASS package is loaded into a dataframe called veggy. Complete this report by answering the following two questions  
 
### Is there a difference in average VitC between c39 and c52 cultivation methods?  

$H_0$: There is no difference in the average vitaminC content between c39 and c52

$H_A$: There is a difference in the average vitaminC content between c39 and c52

# Methods

VitC ~ Cult
VitC is an integer which makes it numerical 
Cult is a factor which makes it categorical
Use file Num~Cat

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method.!-->

# Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
boxplot(VitC~Cult,data=veggy)
```


The Graphical Descriptive Results show us the difference between VitC in c39 and c52. It shows us that VitC in c52 is greater than in c39.

### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
favstats(VitC~Cult,data=veggy)
```

The average for vitc in c39 is 51.5.
The average for vitc in c52 is 64.4.

## Inferential Results

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->

```{r}
t.test(VitC~Cult,data=veggy)
```

The p-value is .00000003, which is less than 0.05
We then reject the null hypothesis and conclude vitc c52 is better than vitc c39

# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->

I looked at the difference in vitc for c39 and c52. I then concluded that c52 is better than c52 as the mean for c52 is 64.4 and the mean for c39 is 51.4.The inferential results then told us the p-value is .00000003 which is less than 0.05. Thus, we reject the null hypothesis as there is a difference in the VitC in c39 and c52, c52 is better than c39. 